Meta-analysis fear learning

### 2022-03-01 manuscript/manuscript.Rmd
update 2022-03-01 18:06:36

```{r setup, include=FALSE}
run_everything = FALSE
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r prepdata, eval=run_everything}
library(metafor)
library(pema)
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
load_data()
dat$Process <- ordered(dat$Process, levels = unique(dat$Process))
processes <- levels(dat$Process)
totaln <- dat[!duplicated(dat$article.code), c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group", "Process")]
totaln <- sapply(processes, function(p){ sum(totaln[totaln$Process == p, -3], na.rm = TRUE)})

@@

@@

```{r threelev, echo=FALSE, warning=FALSE, message=FALSE, results="hide", eval = run_everything}
mlm <- lapply(processes, function(p){
  df <- dat[dat$Process == p, ]
  #Conduct meta-analyses
  #model.mods <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_es), data=df) 
  mod <- rma(df$yi, df$vi) 
confints <- confint(mod)

@@

tb <- lapply(1:length(processes), function(i){
  tb <- mlm[[i]]$res
  tb <- rbind(tb, data.frame(Variance = "I2",
                             estimate.intrcpt = mlm[[i]]$mod$I2,
                             ci.lb = NA,
                             ci.ub = NA,
                             V4 = mlm[[i]]$mod$QEp))
  tb$Process <- processes[i]
  tb
})
tb <- do.call(rbind, tb)
tb$CI <- NA
tb$CI[!is.na(tb$ci.lb)] <- tidySEM::conf_int(lb = tb$ci.lb[!is.na(tb$ci.lb)], ub = tb$ci.ub[!is.na(tb$ci.lb)], digits = 2)
tb[c("ci.lb", "ci.ub")] <- NULL
names(tb) <- c("Parameter", "Estimate", "p", "Process", "CI")
write.csv(tb, "tab_overall.csv", row.names = FALSE)
```
```{r, include = FALSE}
num_effect_sizes <- table(table(dat$article.code))
```

@@

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  df <- dat[dat$Process == p, ]
  df[refcat$Variable] <- lapply(refcat$Variable, function(n){
    v <- df[[n]]
    v <- relevel(v, ref = refcat$Reference[refcat$Variable == n])
    droplevels(v)
  })
  # refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
  # names(refcat) <- c("Variable", "Reference")
  df_mods <- df[mods]
  constcols <- sapply(df_mods, function(i){length(unique(i))}) == 1
  df_mods <- df_mods[, !constcols, drop = FALSE]
  modmat <- model.matrix(~., df_mods)
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_notcentered,
             vi = df$vi,
             mods = modmat)
  vifs <- vif(res)
  saveRDS(res, paste0("rma_", p, ".RData"))
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(NA, vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

@@

```{r, results = "asis", eval = FALSE}
for(i in 1:length(processes)){
  p <- processes[i]
  tb <- modres[[i]]$brma
  tb$format <- as.integer(tb$p == "*")
  print({datatable(tb, rownames= FALSE, caption = paste0("Bayesian regularized meta-regression coefficients for ", p), options = list(
              "pageLength" = nrow(tb))) |>
  formatRound(columns=c('Estimate', 'p'), digits=2)})
}
htmltools::tagList(
  lapply(1:length(processes), function(i) {
    p <- processes[i]
    tb <- modres[[i]]$brma
    tb$format <- as.integer(tb$p < .05)
    formatStyle(
      formatRound(
        datatable(
          tb,
          rownames = FALSE,
          caption = paste0("Bayesian regularized meta-regression coefficients for ", p),
          options = list(columnDefs = list(list(
            targets = 7, visible = FALSE
          )),
          "pageLength" = nrow(tb))
        ),
        columns = c('Estimate', "se"),
        digits = 2
      ),
      "format",
      target = "row",
      backgroundColor = styleEqual(c(0, 1), c('gray', 'white'))
    )
  })
)

@@

<!-- predictie intervallen van elke categorie een goede manier is om de data te visualiseren en de data duidelijk over te brengen op de lezer. -->
```{r, eval = run_everything}
refcat <- structure(list(Variable = c("ssri", "freq", "disease", "species", "test"
), Reference = c("FLX", "chronic", "stress", "rat", "CF")), class = "data.frame", row.names = c(NA, 
-5L))
library(ggridges)
for(p in processes){
  res <- readRDS(paste0("pma_", p, ".RData"))
  pred <- pema:::predict.brma(res, newdata = res$X, type = "samples")
  vars <- c("ssri", "freq", "disease", "species", "test")
  vars <- vars[sapply(vars, function(v){any(grepl(v, colnames(res$X)))})]
  for(v in vars){
    catdf <- res$X[, startsWith(colnames(res$X), v), drop = F]
    splt <- apply(catdf, 1, which.max) + 1
    splt[rowSums(catdf == 0) == ncol(catdf)] <- 1
    labs <- c(refcat$Reference[refcat$Variable == v],
              unique(gsub(".", "", gsub(v, "", grep(paste0("^", v), colnames(res$X), value = T)), fixed = TRUE)))
    splt <- factor(splt, labels = labs)
    df_plot <- do.call(rbind, lapply(levels(splt), function(l){
      data.frame(Value = as.vector(pred[splt == l, ]),
                 Group = l)
    }))
    meds <- tapply(df_plot$Value, df_plot$Group, median)
    postplot <- ggplot(df_plot, aes(x = Value, y = Group)) +
      geom_density_ridges(scale = 1, alpha = 0) +
      geom_segment(data = data.frame(x = meds, xend = meds, y = 1:length(meds), yend = (2:(length(meds)+1))), aes(x = x, xend = xend, y = y, yend = yend), inherit.aes = F, colour = "skyblue3", size = 1) +
      theme_bw() +
      scale_y_discrete(expand =c(0,0))+
      labs(title = p,
           x = paste0("Posterior predicted effect size"),
           y = v)
    ggsave(filename = paste0("group_plot_", v, "_", p, ".png"), plot = postplot, device = "png")
  }
}
```

>>>>

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = FALSE
sens_papers <- "{{sens_study}}" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r prepdata, eval=run_everything}
library(metafor)
library(pema)
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
load_data()
if(sensitivity){
  dat <- dat[!dat$article.code %in% sens_papers, ]
}
dat$Process <- ordered(dat$Process, levels = unique(dat$Process))
processes <- levels(dat$Process)
totaln <- dat[!duplicated(dat$article.code), c("number.of.animals.in.control.group", "number.of.animals.in.intervention.group", "Process")]
totaln <- sapply(processes, function(p){ sum(totaln[totaln$Process == p, -3], na.rm = TRUE)})

@@

```{r, results="asis"}
print("**This is a sensitivity analysis; the study {{sens_study}} has been removed from the data.")
```

@@

```{r threelev, echo=FALSE, warning=FALSE, message=FALSE, results="hide", eval = run_everything}
mlm <- lapply(processes, function(p){
  print(p)
  df <- dat[dat$Process == p, ]
  if(nrow(df) == 0) return(NULL)
  #Conduct meta-analyses
  #model.mods <- rma.mv(yi, vi, random = list(~ 1 | id_study, ~ 1 | id_es), data=df)   
  mod <- rma(df$yi, df$vi) 
confints <- confint(mod)

@@

tb <- lapply(1:length(processes), function(i){
  if(is.null(mlm[[i]])) return(NULL)
  tb <- mlm[[i]]$res
  tb <- rbind(tb, data.frame(Variance = "I2",
                             estimate.intrcpt = mlm[[i]]$mod$I2,
                             ci.lb = NA,
                             ci.ub = NA,
                             V4 = mlm[[i]]$mod$QEp))
  tb$Process <- processes[i]
  tb
})
tb <- do.call(rbind, tb)
tb$CI <- NA
tb$CI[!is.na(tb$ci.lb)] <- tidySEM::conf_int(lb = tb$ci.lb[!is.na(tb$ci.lb)], ub = tb$ci.ub[!is.na(tb$ci.lb)], digits = 2)
tb[c("ci.lb", "ci.ub")] <- NULL
names(tb) <- c("Parameter", "Estimate", "p", "Process", "CI")
write.csv(tb, "tab_overall.csv", row.names = FALSE)
```
```{r, include = FALSE}
num_effect_sizes <- table(table(dat$article.code))
```

@@

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  df <- dat[dat$Process == p, ]
  if(nrow(df) == 0) return(NULL)
  df[refcat$Variable] <- lapply(refcat$Variable, function(n){
    v <- df[[n]]
    v <- relevel(v, ref = refcat$Reference[refcat$Variable == n])
    droplevels(v)
  })
  # refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
  # names(refcat) <- c("Variable", "Reference")
  df_mods <- df[mods]
  constcols <- sapply(df_mods, function(i){length(unique(i))}) == 1
  df_mods <- df_mods[, !constcols, drop = FALSE]
  modmat <- model.matrix(~., df_mods)
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_notcentered,
             vi = df$vi,
             mods = modmat)
  vifs <- vif(res)
  saveRDS(res, paste0("rma_", p, ".RData"))
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(NA, vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

@@

```{r, results = "asis", eval = FALSE}
for(i in 1:length(processes)){
  p <- processes[i]
  if(is.null(modres[[i]])) next
  tb <- modres[[i]]$brma
  tb$format <- as.integer(tb$p == "*")
  print({datatable(tb, rownames= FALSE, caption = paste0("Bayesian regularized meta-regression coefficients for ", p), options = list(
              "pageLength" = nrow(tb))) |>
  formatRound(columns=c('Estimate', 'p'), digits=2)})
}
htmltools::tagList(
  lapply(1:length(processes), function(i) {
    p <- processes[i]
    tb <- modres[[i]]$brma
    tb$format <- as.integer(tb$p < .05)
    formatStyle(
      formatRound(
        datatable(
          tb,
          rownames = FALSE,
          caption = paste0("Bayesian regularized meta-regression coefficients for ", p),
          options = list(columnDefs = list(list(
            targets = 7, visible = FALSE
          )),
          "pageLength" = nrow(tb))
        ),
        columns = c('Estimate', "se"),
        digits = 2
      ),
      "format",
      target = "row",
      backgroundColor = styleEqual(c(0, 1), c('gray', 'white'))
    )
  })
)

@@

<!-- predictie intervallen van elke categorie een goede manier is om de data te visualiseren en de data duidelijk over te brengen op de lezer. -->
```{r, eval = run_everything}
refcat <- structure(list(Variable = c("ssri", "freq", "disease", "species", "test"
), Reference = c("FLX", "chronic", "stress", "rat", "CF")), class = "data.frame", row.names = c(NA, 
-5L))
library(ggridges)
for(p in processes){
  if(is.null(modres[[p]])) next
  res <- readRDS(paste0("pma_", p, ".RData"))
  pred <- pema:::predict.brma(res, newdata = res$X, type = "samples")
  vars <- c("ssri", "freq", "disease", "species", "test")
  vars <- vars[sapply(vars, function(v){any(grepl(v, colnames(res$X)))})]
  for(v in vars){
    catdf <- res$X[, startsWith(colnames(res$X), v), drop = F]
    splt <- apply(catdf, 1, which.max) + 1
    splt[rowSums(catdf == 0) == ncol(catdf)] <- 1
    labs <- c(refcat$Reference[refcat$Variable == v],
              unique(gsub(".", "", gsub(v, "", grep(paste0("^", v), colnames(res$X), value = T)), fixed = TRUE)))
    splt <- factor(splt, labels = labs)
    df_plot <- do.call(rbind, lapply(levels(splt), function(l){
      data.frame(Value = as.vector(pred[splt == l, ]),
                 Group = l)
    }))
    meds <- tapply(df_plot$Value, df_plot$Group, median)
    postplot <- ggplot(df_plot, aes(x = Value, y = Group)) +
      geom_density_ridges(scale = 1, alpha = 0) +
      geom_segment(data = data.frame(x = meds, xend = meds, y = 1:length(meds), yend = (2:(length(meds)+1))), aes(x = x, xend = xend, y = y, yend = yend), inherit.aes = F, colour = "skyblue3", size = 1) +
      theme_bw() +
      scale_y_discrete(expand =c(0,0))+
      labs(title = p,
           x = paste0("Posterior predicted effect size"),
           y = v)
    ggsave(filename = paste0("group_plot_", v, "_", p, ".png"), plot = postplot, device = "png")
  }
}
```
